The Lost Vaults: Uneasy Alliance\\\small{An online multi-user Dungeon Client and Server.}\\\small{Project Proposal for group 4}

### 2014-05-04 doc/ProposalSrc/lostvaults.tex
Updated proposal after proofreading.

\tableofcontents
\listoffigures
\newpage
\section{Introduction}
Concurrency is becoming a more and more important facet of software development as computers rely more heavily on parallel processing and the way we write programs has to change to face 
the challenges that follow making use of this increase in processing power. As a way for us to explore these challenges and their solutions, we opted to work on a server-client 
system over a TCP/IP network connection. The problem we attempt to solve is maintaining a responsive environment for multiple, simultaneous connections as well as multiple active and 
independent sections of program logic. We represent this problem through a multi-user dungeon or MUD, a form of online multiplayer game, where we aim to make sure that the server maintains 
stable performance regardless of the number of connected users and we have decided to call this game Lost Vaults.

>>>>

\tableofcontents
\listoffigures
\newpage
\section{Introduction}
Concurrency is becoming a more and more important facet of software development as computers rely more heavily on parallel processing. Because of this the way we write programs has to change 
to tackle the new type of problems that arise from making use of this different kind of architecture. As a way for us to explore these challenges and their solutions, we opted to work on a 
server-client system over a TCP/IP network connection. The problem we attempt to solve is maintaining a responsive environment for multiple, simultaneous connections as well as multiple 
active and independent sections of program logic. We represent this problem through a multi-user dungeon or MUD, a form of online multiplayer game, where we aim to make sure that the server maintains 
stable performance regardless of the number of connected users and we have decided to call this game Lost Vaults.
